Agile Inter-team Software Development

### 2019-01-21 Draft/Parts/Abstract.tex
Make abstract more clear.

%Problem statement
As the complexity of software development increases, companies relying on agile processes are asked to apply agile at large scale.
However, this conflicts with the basic tenets of agile which focus on interaction and flexibility.
%Proposed Solutions
A typical solution is to run several agile teams in parallel, with appropriate adaptations in process, technology, and architecture.
%Contribution/Method
In this paper, we review the use of agile for large projects, and appropriate adaptations.

>>>>

%Problem statement
As the complexity of software development increases, companies relying on agile processes are asked to apply agile at large scale.
A typical approach is to run several agile teams in parallel, however, this can conflict with the basic tenets of agile which focus on interaction and flexibility.
%Proposed Solutions
A key aspect in this transition is maintaining quality communication to ensure progress, which can be addressed with appropriate adaptations in process, technology, and architecture.
%Contribution/Method
In this paper, we review the use of agile for large projects, and appropriate adaptations.
